

\documentclass[a4paper]{deedy-resume}

\begin{document}
% --
\namesection{Andy}{Burton}{ % Your name
%\urlstyle{same}\url{http://andyburton0912.github.io} \\ % Your website, LinkedIn profile or other web address
\href{mailto:andy.burton@engineer.com}{andy.burton@engineer.com} | 07749941261 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills} 

\sectionspace
\subsection{Technologies}
\textbullet{}\descript{Active Directory}
\textbullet{}\descript{Windows Server}
\textbullet{}\descript{Windows 7, 8 and 10}
\textbullet{}\descript{Cisco Routers and switching}
\textbullet{}\descript{Cisco Call Manager Express}
\textbullet{}\descript{Virtualisation Technologies including Hyper V and vmware}
\textbullet{}\descript{Gamma Horizon Hosted IP Phone System}
\textbullet{}\descript{Backup solutions Veeam and Virtual One}
\textbullet{}\descript{Office 365}
\textbullet{}\descript{PRTG Network Monitor}
\textbullet{}\descript{Cisco Meraki Network Devices}
\textbullet{}\descript{Powershell}
\sectionspace % Some whitespace after the section

\sectionspace % Some whitespace after the section
\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace


%------------------------------------------------
% Certifications
%------------------------------------------------

\section{Certifications}

\textbullet{}\descript{Cisco Certified Network Associate Routing and Switching}
\textbullet{}\descript{Azure Administrator Associate  (Working Towards)}

\sectionspace % Some whitespace after the section
\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace
%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{GCSEs}
\descript{9 GCSE passes (including English and
Mathematics}
\sectionspace % Some whitespace after the section
\sectionspace
\subsection{GNVQ}
\descript{Intermediate GNVQ Business Studies -
pass}

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.60\textwidth} % The right column takes up 66% of the text width of the page
\section{Personal Summary}
\location {I take pride in ensuring that all of my tasks are carried out to a very high standard. I am an independent and self-motivated thinker and am capable of using my own judgment and initiative to plan and organise my workload. I am a quick and eager learner and am able to take on board new processes and procedures with relative ease. I have passed both my Cisco CCENT and CCNA and am currently studying towards my Azure Administrator Associate certification and also learning Python. I am very flexible in my approach to my work and am always eager to embrace any changes in processes and procedures}
%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{CMC IT}
\descript{| Techinical Engineer}
\location{March 2018 - Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Providing 3rd/2nd Line support for users and being the main escalation point for the helpdesk, monitoring client infrastructure with monitoring software and performing any maintenance required.
\sectionspace
\begin{tightitemize}
\item Implemented and rolled out Broadband and IP Phone system to 12 different sites for a client 
\item Ensured backups have run successfully and resolving any issues with the backups.
\item Setting up monitoring and resolving any issues relating to the various network devices and servers 
\item Working on Projects and liasing with the IT Project Manager
\item Building installing and maintaining windows servers 
\item Administering office 365 
\item Setting up and administering Gamma Horizon Phone System.
\item Involved in installing and configuring network in new building for client prior to move.
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Oyez Speech}
\descript{| Client Support Executive}
\location{October 2017 - March 2018}
\item Providing support and training for users of Oyez Speech software and Phillips and Olympus hardware 
\sectionspace
\begin{tightitemize}
\item Testing hardware which has been returned for any faults 
\item Testing software and reporting bugs to development team 
\item Creating usernames/security settings.
\item Advising Clients IT teams on issues and how to resolve.
\item Co-ordinating with 3rd party IT desks
\item Meeting SLAs \& KPIs
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{clanwilliam Health}
\descript{| Service Delivery Executive}
\location{July 2014 – October 2017}
\item Configuring and installing DGL Practice Manager Software and Training users both on site and remotely 
\sectionspace
\begin{tightitemize}
\item Deliver training services to customers in UK, Ireland and elsewhere
\item Work closely with colleagues in Service Delivery, Sales, Support and
Development in the organizing and delivery of training services
\item Learn and self-train on products and releases as required.
\item Contribute to business improvement initiatives in the training team, Service Delivery and the wider organization.
\item Creating and disabling accounts in RSA for clients and assigning Tokens
\end{tightitemize}
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column


\newpage
%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------



\sectionspace % Some whitespace after the section

\sectionspace % Some whitespace after the section
\sectionspace

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.60\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience - Continued
%------------------------------------------------


\runsubsection{clanwilliam Health}
\descript{| Application Support Analyst}
\location{July 2014 – July 2015}
\item Provide support to the users of our DGLPM Practice Manager program over the
telephone, email and remotely. Work with the team to achieve our Grade of
Service and hit our targets. Fix or escalate issues and queries to the 2nd  line
support team. 
\sectionspace
\begin{tightitemize}
\item Providing support for Practice Manager Software and Microsoft Word.
\item Taking calls from clients and diagnosing and solving faults on their behalf
\item Logging calls on CRM
\item Restoring corrupt databases
\item Helping/training users on Practice Manager Software
\item Helping user log-in with rsa key fobs
\item Using Windows server 2003 and 2010 to remotely access users sessions to resolve issues
\item Using Citrix to log into clients networks or Dameware to remotely access
their PCs
\item Assisting users with installation issues
\item Setting up remote desktop connections
\item Helping with printing issues from the server
\item Creating usernames/security settings
\item Setting up email accounts within Microsoft Outlook
\item Co-ordinating with 3rd party IT desks
\item Meeting SLAs &amp; KPIs
\item Data transfers
\item Updating users software and reporting on any bugs/issues
\end{tightitemize}
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\runsubsection{Computa Center}
\descript{| First Line Analyst/Request Management Analyst}
\location{July 2013 - July 2014}
\item Provide support to the users over the telephone, email and remotely. Work with
the team to achieve our targets. Fix or escalate issues and queries to the relevant
team.
\sectionspace
\begin{tightitemize}
\item Taking calls from clients and diagnosing and solving faults on their behalf 
\item Logging calls onto BMC Remedy 
\item Assigning incidents to the appropriate teams
\item Creating and disabling accounts in Active Directory for clients
\item Using CITRIX on a daily basis to access clients’ networks
\item Creating and disabling email accounts and shared mailboxes via Exchange
Management Console
\item Setting up and changing settings for EAS archiving via EAS Administrator
\item Distributing software via SCCM
\item Manual installation/removal of software and printers
\item Creating HR records in SAP
\item Administering the team mailbox and booking call-backs into the team
calendar
\item Following up pending requests.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column
\end{document}